\documentclass[a4paper,12pt]{article}
\usepackage{anysize}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{pdflscape}
\usepackage[T1]{fontenc}
\usepackage[none]{hyphenat}%%%%
\setlength{\headheight}{15pt}
\marginsize{2.5cm}{2.5cm}{1cm}{1cm}
\setlength{\parskip}{10pt}
\setlength\parindent{0pt}
\def\uuid{286fe3b0-2235-11e4-8c21-0800200c9a66}
\def\authorname{Mike Jones}
\def\authoremail{mike.a.jones@me.com}
\def\shorttitle{Grant by Thomas Chauntrell to Elisha Jeusse, chaplain, Edmund Seggeford, Richard Tappe and John Leylond of two tenements on St Nicholas Street, Bristol. 13 December, 1506.}
\def\abstract{Grant by Thomas Chauntrell to Elisha Jeusse, chaplain, Edmund Seggeford, Richard Tappe and John Leylond of two tenements on St Nicholas Street, Bristol. 13 December, 1506.}
\def\pubdate{August 2014}
\def\archivename{Bristol Record Office}
\def\archiveabbr{BRO}
\def\archiverefno{5139/155}
\def\archivedoctitle{Thomas, son and heir of William Chauntrell and Emmote his wife, to Elisha Jeusse, chaplain, Edmund Seggeford, Richard Tappe and John Leylond Grant of two tenements in St Nicholas' Street, adjoining to a house occupied by Robert Thorne and belonging to Witham Priory, and also adjoining a house of Richard Vaghan's called le Bakers hall}
\hypersetup{
	pdfinfo={
	    Author={\authorname},
	    AuthorEmail={\authoremail},
	    Title={\shorttitle},
	    Subject={\abstract},
	    Keywords={Thorne, Bristol, Deed},
		UUID={\uuid},
		PubDate={\pubdate},
		Language={Latin},
		SubjectYear={1506},
		SubjectDate={13 December 1506},
		Archive={\archivename},
		ArchiveAbbr={\archiveabbr},
		ArchiveRefNo={\archiverefno},
		ArchiveDocTitle={\archivedoctitle},
		License={http://creativecommons.org/licenses/by/4.0/}
	}
}
\begin{document}
\title{\Large \shorttitle\\\normalsize \vspace{1em} \archivename \hspace{0 mm}, \archiverefno \hspace{1 mm}}\vspace{-5em}
\author{\small Edited by \authorname \hspace{0 mm} (\authoremail)}
\date{\small \pubdate}
\maketitle

\section*{Introduction}
\abstract

The tenements are located between a tenement occupied by Robert Thorne (d. 1519) and owned by the priory of Witham, Somerset, on one side and a tenement owned by Richard Vaghan and called `le Bakers Hall' on the otherside.

\section*{Editorial Note}

The transcription was made from a digital photograph. Original punctuation and spelling are preserved. The end of lines are indicated by a vertical bar. Superscript characters are lowered and contractions expanded with supplied letters italicised. The thorn (\th\ or y) is replaced with `th' and a terminal graph with `es'. The ampersand brevigraph is silently expanded to `and' in English and `et' in Latin. Letters within square brackets are supplied by the editor. Engrossed hand are shown in bold text.

\section*{Text}
\begin{sloppypar}
\textbf{Sciant} p\textit{re}sentes et futuri q\textit{uo}d ego Thomas Chauntrell filius et heres Will\textit{elm}i Chauntrell et Emmote ux\textit{o}r\textit{i}s eius dedi concessi | et hac p\textit{re}senti carta mea confirmavi Heliseo Jeusse Capellano Edmundo Seggeford Ricardo Tappe et Joh\textit{ann}i Leylond totu\textit{m} illa duo\footnote{\textit{duo} is inserted above \textit{tenementa}} Tenementa | mea scituata in Villa Bristoll in quodam vico ib\textit{ide}m vocat\textit{o} Seynt Nicholas Strete inter ten\textit{emen}tum Prioris et Conventus domus Cartusien\textit{sis} | de Witham in quo Robertus Thorne modo inhabitat ex parte occident\textit{a}li et ten\textit{ement}um Ric\textit{ard}i Vaghan mercatoris ex parte orient\textit{a}li. Et extend\textit{it} | se a vico p\textit{re}dict\textit{o} anterius ex parte austral\textit{i} usq\textit{ue} unu\textit{m} ten\textit{emen}tum d\textit{ic}ti Ric\textit{ard}i Vaghan vocat\textit{um} le Bakers Hall et aliud ten\textit{emen}tum Joh\textit{ann}is Kemys de Oldbury | Gentleman posterius ex parte boriali. Habend\textit{um} et tenend\textit{um} Ten\textit{emen}ta p\textit{re}dict\textit{a} cu\textit{m} suis p\textit{er}tin\textit{enciis} p\textit{re}fat\textit{is} Heliseo Edmundo Ric\textit{ard}o et Joh\textit{ann}i heredib\textit{us} et assign\textit{atis} | eor\textit{um} imperpetuu\textit{m} De capital\textit{ibus} d\textit{omi}nis feod\textit{orum} ill\textit{orum} per s\textit{er}vicia inde debit\textit{a} et de iure consuet\textit{a}. Et ego vero p\textit{re}d\textit{ic}tus Thomas Chauntrell et heredes mei | p\textit{re}dict\textit{a} ten\textit{emen}ta cum suis p\textit{er}tin\textit{enciis} p\textit{re}fatis Heliseo Jeusse capellano Edmundo Seggeford Ric\textit{ard}o Tappe et Joh\textit{ann}i Leylond heredib\textit{us} et assign\textit{atis} suis contr\textit{a} om\textit{n}es gentes | Warantizabimus acquietabimus et imperpetuu\textit{m} defendemus per p\textit{re}sentes. \textbf{Ac insuper} Sciatis me p\textit{re}d\textit{ic}t\textit{u}m Thomam Chauntrell attornasse | constituisse et in loco meo posuisse di\textit{le}ctos michi in \textit{christ}o Will\textit{elmu}m Stowte et Roger\textit{um} Garbet meos veros et legittimos Attornat\textit{os} coniunctim et divism Ad | intrand\textit{um} et possessionem capiend\textit{um} De et in ten\textit{emen}t\textit{a} p\textit{re}dict\textit{is} cum suis p\textit{er}tin\textit{enciis}. Et post huiusmodi ingressum et possessionem sic capt\textit{am} et habit\textit{am} ad delib\textit{er}and\textit{am} inde | Vice et no\textit{m}i\textit{n}e meo plenam Ac pacificam possessionem et seismam p\textit{re}fatis Heliseo Jeusse Edmu\textit{n}do Seggeford Ric\textit{ard}o Tappe and Joh\textit{ann}i Leylond aut eor\textit{um} alicui | sive aliquib\textit{us} iuxta vim formam et effectu\textit{m} huius p\textit{re}sentis Carte mee eis inde confecte. Rat\textit{um} et grat\textit{um} h\textit{ab}entem et h\textit{ab}itur\textit{um} totum et quicquid p\textit{re}d\textit{ic}ti attornati mei | no\textit{m}i\textit{n}e meo fecerint aut eor\textit{um} alter fecerit in p\textit{re}missis. In cuius rei testimoniu\textit{m} huic p\textit{re}senti Carte mee Sigillum meu\textit{m} Apposui Hijs testib\textit{us} Hugone Elyot | Will\textit{el}mo Thorne Clemente Pernaunt et multis Alijs. Dat\textit{um} tertiodecimo die mensis Decembris Anno regni Regis Henrici Septum post conquestum | Anglie Vicesimo secundo.\end{sloppypar}

Thomas Chauntrell

\section*{Translation}

Let [all men] present and future know that I Thomas Chauntrell, son and heir of William Chauntrell and his wife Emmote, have given, granted and by this my present deed confirmed to Elisha Jeusse, chaplain, Edmund Seggeford, Richard Tappe and John Leylond my whole two tenements situated within the town of Bristol in a certain street in that very place called St. Nicholas Street between the tenement of the prior and convent of the Carthusian house of Witham in which Robert Thorne now occupies on the western side and the tenement of Richard Vaghan on the eastern side. And extends itself from the aforesaid street in front on the southern side upto the one tenement of the aforesaid Richard Vaghan called `The Bakers Hall' and another tenement of John Kemnys of Oldbury, gentleman, at the back on the north side. To have and to hold the aforesaid tenements with their appurtenances to the aforesaid Elisha, Edmund, Richard and John, their heirs and assigns forever of the chief lords of those fees by services owned in respect thereof and by right accustomed. And I truely the aforesaid Thomas Chauntrell and my heirs will warrant, acquit and defend forever  against all peoples by the present [charter] the aforesaid tenements with their appurtenances to the aforesaid Elisha Jeusse, chaplain, Edmund Seggeford, Richard Tappe and John Leylond, their heirs and assigns. And moreover know that I the aforesaid Thomas Chauntrell have appointed as attorney and in my place have ordained my beloved in Christ William Stowte and Roger Garbet my true and legitimate attorneys, jointly and seperately, for entering and taking possession of and in the said tenements with their appurtenances. And after this entry and posession thus taken and held to deliver thereof for and in my name full and peaceful possession and seisen to the aforesaid Elisha Jeusse, Edmund Seggeford, Richard Tappe and John Leylond or any of them or any according to the force, form and effect of this my present deed made thereupon; holding and about to hold as right and pleasing all and whatsoever my aforesaid attorneys in my name will have made or one of them will have made in the premisses. In testimony of which matter I have affixed my seal to this my present deed. These being witnesses Hugh Eliot, William Thorne, Clement Pernaunt and many others. Dated the thirteenth day of the month of December the twenty-second year of the reign of King Henry the Seventh of England after the conquest. 

Thomas Chauntrell
\end{document}